dataaimsr: An R Client for the Australian Institute of Marine Science Data Platform API which provides easy access to AIMS Data Platform

### 2021-06-01 paper/paper.Rmd
fixed figure referencing

The first step would be to visualise the dataset. We do this by
mapping all available sites. For example, we download the summary information
for the Sea Water Temperature Loggers dataset using the main function called
`aims_data`. Setting the argument `api_key = NULL` means that `dataaimsr` will
automatically search for the user's API key stored in `.Renviron`.
The `summary` argument should only be used when the
user wants an overview of the available data---this is currently
implemented for the Sea Water Temperature Loggers dataset only. One can
visualise `summary-by-series` or `summary-by-deployment`. The output of
`aims_data` is a `data.frame` of class `aimsdf` with its own plotting
method (Fig. \@ref(fig:summary)):

@@

(ref:fig-summary) Distribution of all temperature logger series around Australian waters.

```{r summary, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-summary)", cache = TRUE}
knitr::include_graphics("summary.png")
```

@@

This example data contains multiple parameters available for this site at the
specified time, and the actual measurements are either raw or
quality-controlled. For monitoring data (i.e. when `summary = NA` in a
`aims_data` call), we can either visualise the data as a time series broken
down by parameter, or a map showing the sites with some summary info. If the
parameters are not specified, then `dataaimsr` will plot a maximum of 4
parameters chosen at random for a time series plot. Alternatively the user can
specify which parameters are to be plotted (Fig. \@ref(fig:wind)).

@@

(ref:fig-wind) Yongala wreck profiles for water pressure and chlorophyll-a between the first and second of January 2018.

```{r wind, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-wind)", cache = TRUE}
knitr::include_graphics("wind.png")
```

@@

The Time Series Explorer (https://apps.aims.gov.au/ts-explorer/) is an
interactive web-based application that visualises large time series datasets.
The application utilises the AIMS Data Platform API to dynamically query data
according to user selection and visualise the data as line graphs. Series are
able to be compared visually. For large series, data are aggregated to daily
averages and displayed as minimum, maximum and mean. When the user 'zooms in'
sufficiently, the data will be displayed as non-aggregate values
(Fig. \@ref(fig:tssa)). This technique is being used to ensure the application
performs well with large time series.

(ref:fig-tssa) Interactive discovery and visualisation of data series.

```{r tssa, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-tssa)", cache = TRUE}
knitr::include_graphics("tssa.png")
```

The user can then download the displayed data as CSV or obtain a R code
snippet that shows how to obtain the data using the dataaimsr package
(Fig. \@ref(fig:tssb)). In this way, a user can easily explore and discover
datasets and then quickly and easily have this data in their R environment for
additional analysis.

(ref:fig-tssb) Download/Export displayed data via R snippet.

```{r tssb, echo = FALSE, out.width = "100%", fig.cap="(ref:fig-tssb)", cache = TRUE}
knitr::include_graphics("tssb.png")
```

>>>>

The first step would be to visualise the dataset. We do this by
mapping all available sites. For example, we download the summary information
for the Sea Water Temperature Loggers dataset using the main function called
`aims_data`. Setting the argument `api_key = NULL` means that `dataaimsr` will
automatically search for the user's API key stored in `.Renviron`.
The `summary` argument should only be used when the
user wants an overview of the available data---this is currently
implemented for the Sea Water Temperature Loggers dataset only. One can
visualise `summary-by-series` or `summary-by-deployment`. The output of
`aims_data` is a `data.frame` of class `aimsdf` with its own plotting
method \autoref{fig:summary}:

@@

![Distribution of all temperature logger series around Australian waters.\label{fig:summary}](summary.png)

@@

This example data contains multiple parameters available for this site at the
specified time, and the actual measurements are either raw or
quality-controlled. For monitoring data (i.e. when `summary = NA` in a
`aims_data` call), we can either visualise the data as a time series broken
down by parameter, or a map showing the sites with some summary info. If the
parameters are not specified, then `dataaimsr` will plot a maximum of 4
parameters chosen at random for a time series plot. Alternatively the user can
specify which parameters are to be plotted \autoref{fig:wind}.

@@

![Yongala wreck profiles for water pressure and chlorophyll-a between the first and second of January 2018.\label{fig:wind}](wind.png)

@@

The Time Series Explorer (https://apps.aims.gov.au/ts-explorer/) is an
interactive web-based application that visualises large time series datasets.
The application utilises the AIMS Data Platform API to dynamically query data
according to user selection and visualise the data as line graphs. Series are
able to be compared visually. For large series, data are aggregated to daily
averages and displayed as minimum, maximum and mean. When the user 'zooms in'
sufficiently, the data will be displayed as non-aggregate values
\autoref{fig:tssa}. This technique is being used to ensure the application
performs well with large time series.

![Interactive discovery and visualisation of data series.\label{fig:tssa}](tssa.png)

The user can then download the displayed data as CSV or obtain a R code
snippet that shows how to obtain the data using the dataaimsr package
\autoref{fig:tssb}. In this way, a user can easily explore and discover
datasets and then quickly and easily have this data in their R environment for
additional analysis.

![Download/Export displayed data via R snippet.\label{fig:tssb}](tssb.png)
